A theoretical analysis of the Keep Network random beacon using agent based modeling \\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2019-09-09 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
stochastic assumptions

@@

\subsection{Terminology}
Node: A computational entity with memory and computational power sufficient to to run a 
keep client

Node Owner: may own 1 or more nodes and can allocate different levels of stake to each node
owned

Stake: A bond that make a node eligible to participate in a group

Group: A collection of nodes who have successfully completed DKG together

DKG (Distributed Key Generation): The processes of generating keys for each node enabling
them to sign using Keep's version of Threshold ECDSA \cite{Gennaro2018}.

Signature: The process of securely generating a random number using Threshold ECDSA \cite{Gennaro2018}

Ownership Percent: The level of ownership a specific entity has in a group or signature

Lynchpin: A node who's ownership exceeds the maximum malicious threshold

\subsection{Runs}
\begin{itemize}

\item Single run
\item Multiple runs

@@

\subsection{Assumptions}
\begin{itemize}
\item Stochastic Assumptions
\item Ticket distribution Assumptions
\item Model Assumptions
\end{itemize}

>>>>

\subsection{Key Terms}
\begin{itemize}
\item Node: A computational entity with memory and computational power sufficient to to run a 
keep client

\item Node Owner: may own 1 or more nodes and can allocate different levels of stake to each node
    owned

\item Stake: A bond that make a node eligible to participate in a group

\item Group: A collection of nodes who have successfully completed DKG together

\item DKG (Distributed Key Generation): The processes of generating keys for each node enabling
    them to sign using Keep's version of Threshold ECDSA \cite{Gennaro2018}.

\item Signature: The process of securely generating a random number using Threshold ECDSA \cite{Gennaro2018}

\item Ownership Percent: The level of ownership a specific entity has in a group or signature

\item Lynchpin: A node who's ownership exceeds the maximum malicious threshold
\end{itemize}

@@

Usually steps measure a change in time. Therefore for our simulation we assume
1 step = 1 block.

\subsection{Runs}
We perform two sets of experiments to answer our research questions. 
\begin{itemize}

\item Single run: Our single run of 1000 steps provide a first look at the 
performance of the sim, quickly. We also use this first experiment to evaluate
when steady state behavior could occur. We also perform some initial evaluations
of the impact of different stake distributions.

\item Multiple runs: The second experiment consists of multiple runs with varying 
parameters. For each change in parameter we perform 6 runs. By varying parameters 
in these runs we attempt to identify sensitivity. We measure this sensitivity after
the start of steady state behavior which we identify in the single run.

@@

\subsection{Assumptions}

\textit{Stochastic Assumptions}
To simplify the model we make stochastic assumptions for exogenous processes.

\begin{itemize}

\item Node Connection Delay: We apply a random uniform distribution to a user specified range (NEED JUSTIFICATION OR A JUSTIFIED SAMPLING)
\item Node Connection Failure: This is one of the parameters we intend to adjust to test for sensitivity. Therefore we
randomly pick a percentage of nodes to fail using a uniform distribution.
\item Node Death: We uniform randomly pick nodes to die at a user specified rate.
\item Signature Delay: A delay between when a signature is triggered and when it is executed. We use a poisson distribution. (NEED JUSTIFICATION or REFERENCE)
\item Node Owner Assignment: We use a normal distribution to assign owners to nodes. (NEED JUSTIFICATION)
\end{itemize}

\textit{Ticket distribution} Assumptions
Model Assumptions
